\section{Question 10.5}

\subsection{Question}
Find a community-based question answering site on the Web and ask two
questions, one that is low-quality and one that is high-quality. Describe the answer quality of each question.

\subsection{Results and Discussion}
Yahoo! Answers is the question and answering website I chose to use to complete this exercise.  First, the high quality question I asked was:\\

\blockquote{Were there treaties in place at that time of Russia's annexation of Crimea which were, without doubt, violated by this act?}\\

I deem this question to be of high quality based on grammaticality, spelling and punctuation, as well as the use of concise terminology that may be slightly obscure to an uneducated reader.

It is also a focused question that has a definite set of possible answers.  Either treaties exist that were broken or there weren't, albeit with some amount of flexibility due to legal interpretation.

An example of a good response I received within minutes of posting the question is this:

\blockquote{Absolutely, the Treaty of the Separation of States between Ukraine and Russia (c.1994) gave all Crimea to Ukraine without doubt. By said treaty Russia got to keep it's historic naval base in Crimea... But not an inch more.  However, even in the mid 90's Crimea's population was 98 percent Russian, and Russia did have historic ties there from 1700 on.}

This answer is well thought out and readable.  It references an item that directly answers the question: a treaty that between the Russian Federation, the United States of America, and the United Kingdom concerning the territorial integrity and political independence of Ukraine (among other nations) in exchange for their nuclear disarmament.  The answer also provides some reasoning as to how it could be a justified act in the eyes of the Russian Federation, which adds to the quality of the answer by providing insight from multiple perspectives.

Now, for the poor quality question, I asked:\\

\blockquote{Trump is not russia, y u no belief he got hakerz to do it to us?}\\

Firstly, it begins with a premise that doesn't make semantic sense; I doubt there are many people who would suspect that Trump \textit{is} Russia.  It also lacks focus as to what is being asked for and has no real context and is full of misspellings and terrible grammar.  For these reasons this is a bad question.\\

Correspondingly, the answers were lacking in quality based on content, poor grammar and spelling errors.  Some could even be considered offensive.  Refer to Table \ref{tab:badq} for some sample answers.

\begin{table}[H]
\centering
\begin{tabular}{ | c | }
\hline
Trump is Putin's *****\\
\hline
Ye\\
\hline
we got hakerzed in the ***\\
\hline
no\\
\hline
Penis\\
\hline
\end{tabular}
\caption{Responses to ``Trump is not russia, y u no belief he got hakerz to do it to us?''}
\label{tab:badq}
\end{table}

So there does seem to be a correlation between the quality of the question and the quality of the answers one can expect to receive.  Higher quality questions tend to receive higher quality answers.
